title: "Bibliometrics_indicators" 
output: html_notebook ---

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by
pressing *Ctrl+Alt+I*.
When you save the notebook, an HTML file containing the code and output will be
saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to
preview the HTML file).
The preview shows you a rendered HTML copy of the contents of the editor.
Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead,
the output of the chunk when it was last run in the editor is displayed.


#starting some bibliometrics_indicators based on the order Bibliometrix
#https://cran.r-project.org/web/packages/bibliometrix/vignettes/bibliometrix-vignette.html

#PRODUCTION_INDICATORS

# 1. Annual Scientific Production


```{r}

```


# Most Productive Authors

```{r}

```

# Most Productive Countries (of corresponding authors)

```{r}

```

# Total Citations per Country

```{r}

```


# Most Relevant Sources

```{r}

```


# Most Relevant Keywords

```{r}

```

#COLLABORATION_INDICATORS

#Country Scientific Collaboration

```{r}

```

#Co-Citation Network

```{r}

```

#Keyword co-occurrences

```{r}

```

#Historical Co-Citation Network
```{r}

```


