---
title: "Bibliometrics Indicators Report"
output: html_notebook
---

starting some bibliometrics_indicators based on the order Bibliometrix

https://cran.r-project.org/web/packages/bibliometrix/vignettes/bibliometrix-vignette.html

# Creating the environment

```{r Creating the environment, message=FALSE, warning=FALSE, paged.print=FALSE}
library(xts)
library(lubridate)
```


# Reading data

```{r reading_data}
paper <- read.csv("forest/paper.csv", stringsAsFactors = FALSE)
author <- read.csv("forest/author.csv", stringsAsFactors = FALSE)
paperauthor <- read.csv("forest/paperauthor.csv", stringsAsFactors = FALSE)
journal <- read.csv("forest/journal.csv", stringsAsFactors = FALSE)
paperpublisher <- read.csv("forest/paperpublisher.csv", stringsAsFactors = FALSE)
conference <- read.csv("forest/conference.csv", stringsAsFactors = FALSE)
referencelink <- read.csv("forest/referencelink.csv", stringsAsFactors = FALSE)
address <- read.csv("forest/address.csv", stringsAsFactors = FALSE)
```


# PRODUCTION_INDICATORS

## 1. Annual Scientific Production


```{r}
anual_production_table <- data.frame(table(paper$year_published),
                                     stringsAsFactors = FALSE)
names(anual_production_table) <- c("date", "count")
anual_production_table$date <- as.character(anual_production_table$date)
dates <- anual_production_table$date
values <- anual_production_table$count
anual_production_table.xts <- as.xts(values, order.by = as.Date(dates, "%Y"))
plot(anual_production_table.xts, main = "AMID Anual Production Papers")
```


## Most Productive Authors

```{r}

most_prod_author_1 <- data.frame(table(paperauthor$id_author), 
                                 stringsAsFactors = FALSE)
most_prod_author_2 <- data.frame(author = most_prod_author_1$Var1,
                                 count = most_prod_author_1$Freq,
                                 stringsAsFactors = FALSE)


```

## Most Productive Countries (of corresponding authors)

```{r}

```

## Total Citations per Country

```{r}

```


##Most Relevant Sources

```{r}

```


## Most Relevant Keywords

```{r}

```

# COLLABORATION_INDICATORS

## Country Scientific Collaboration

```{r}

```

## Co-Citation Network

```{r}

```

## Keyword co-occurrences

```{r}

```

## Historical Co-Citation Network
```{r}

```


